Wetting of the tarsal adhesive fluid controls underwater adhesion in ladybug beetles

### 2021-07-13 source/jeb_tex/manuscript.tex
used JEB latex template and ported the manuscript format.
reference style needs correction.

%% LyX 2.3.6 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[english]{achemso}
\setkeys{acs}{keywords = true}
\usepackage[T2A,LGR,T1]{fontenc}
\usepackage{babel}
\usepackage{array}
\usepackage{textcomp}
\usepackage{url}
\usepackage{multirow}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{subscript}
\usepackage[unicode=true,pdfusetitle,
 bookmarks=true,bookmarksnumbered=false,bookmarksopen=false,
 breaklinks=false,pdfborder={0 0 0},pdfborderstyle={},backref=false,colorlinks=false]
 {hyperref}
%\usepackage{lineno}
%\linenumbers

\makeatletter

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.

@@

\author{Pranav Sudersan}

\affiliation{Max Planck Institute for Polymer Research, Ackermannweg 10, 55128
Mainz, Germany}

\author{Michael Kappl}

\affiliation{Max Planck Institute for Polymer Research, Ackermannweg 10, 55128
Mainz, Germany}

\author{Bat-El Pinchasik}

\affiliation{School of Mechanical Engineering, Tel Aviv University, Tel Aviv-Yafo,
Israel}

\author{Hans-J\"{u}rgen Butt}

\affiliation{Max Planck Institute for Polymer Research, Ackermannweg 10, 55128
Mainz, Germany}

\author{Thomas Endlein}

\affiliation{Max Planck Institute for Polymer Research, Ackermannweg 10, 55128
Mainz, Germany}

\email{endlein01@mpip-mainz.mpg.de}

@@

\DeclareRobustCommand{\greektext}{%
  \fontencoding{LGR}\selectfont\def\encodingdefault{LGR}}
\DeclareRobustCommand{\textgreek}[1]{\leavevmode{\greektext #1}}
\ProvideTextCommand{\~}{LGR}[1]{\char126#1}

\DeclareRobustCommand{\cyrtext}{%
  \fontencoding{T2A}\selectfont\def\encodingdefault{T2A}}
\DeclareRobustCommand{\textcyr}[1]{\leavevmode{\cyrtext #1}}

\newcommand{\lyxmathsym}[1]{\ifmmode\begingroup\def\b@ld{bold}
  \text{\ifx\math@version\b@ld\bfseries\fi#1}\endgroup\else#1\fi}

%% Because html converters don't know tabularnewline
\providecommand{\tabularnewline}{\\}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
\SectionNumbersOn
%\setkeys{acs}{doi = true}
\setkeys{Gin}{width=\linewidth}
\usepackage{subcaption}
\usepackage[pagewise]{lineno}
\linenumbers

\makeatother

\section*{Summary statement}

Fluid-mediated adhesion seen in animals such as ladybug beetles allow them to attach to surfaces not just in air but also in underwater conditions.

\begin{abstract}

Many insects can climb smooth surfaces using hairy adhesive pads on their legs mediated by tarsal fluid secretions. It was previously shown that a terrestrial beetle can even adhere and walk underwater. The naturally hydrophobic hairs trap an air bubble around the pads, allowing the hairs to make contact to the substrate like in air. However, it remained unclear to what extent such an air bubble is necessary for underwater adhesion. To investigate the role of the bubble, we measured the adhesive forces in individual legs of live but constrained ladybug beetles underwater in the presence and absence of a trapped bubble and compared it with its adhesion in air. Our experiments revealed that on a hydrophobic substrate, even without a bubble, the pads show adhesion comparable to that in air. On a hydrophilic substrate, underwater adhesion is significantly reduced, with or without a trapped bubble. We modelled the adhesion of a hairy pad using capillary forces. Coherent with our experiments, the model demonstrates that the wetting properties of the tarsal fluid alone can determine the ladybugs'  adhesion to smooth surfaces in both air and underwater conditions and that an air bubble is not a prerequisite for their underwater adhesion. The study highlights how such a mediating fluid can serve as a potential strategy to achieve underwater adhesion via capillary forces, which could inspire artificial adhesives for underwater applications.
\end{abstract}

@@

The question on how insects and other small animals climb smooth and slippery
surfaces has fascinated scientists for the past three centuries \cite{RN198,RN59}. We know that such animals are able to adhere by using specialised organs on their feet called adhesive pads. These adhesive pads can generally be described as either ``smooth'' or ``hairy''. Several insect orders including earwigs, flies, and beetles \cite{Gorb:2001b} but also several spiders \cite{Coddington:1991} and arboreal lizards \cite{Williams:1982} bear hairy pads. Hairy pads show 1) compliance to rough surfaces due to their lower effective modulus, 2) angle dependent adhesion due to asymmetric hair geometry and 3) self-cleaning capability \cite{RN20}, which makes them suitable to adhere to most surfaces reversibly. The hairs themselves (setae) can branch into smaller fibrillar units (spatulae) as seen in spiders and lizards but are typically undivided in most insects. The hairs in many insects can however exhibit different tip geometries, including discoidal, spatula shaped or pointed tips, and distributed throughout the pad depending on sex or species\cite{RN19}. Single seta force measurements revealed that discoidal shaped seta show larger pull-off forces than spatula shaped or pointed setae\cite{RN79}, illustrating the role of hair geometry in adhesion. Insect tarsal hairs secrete an adhesion-mediating fluid (``wet adhesion'') while spiders and geckos rely on their dry hairy pads for attachment (``dry adhesion''). In the ``wet adhesion'' case, fluid secretion can enforce adhesion through surface tension and viscous forces \cite{RN201,RN155,RN71}, while, ``dry adhesion'' relies mostly on van der Waals forces \cite{RN202}.

While most of the studies on insect adhesion focused on terrestrial species, underwater insect attachment is much rarer and has been relatively unexplored. Some aquatic insects like diving beetles \cite{Chen:2014} or midge larva \cite{Kang:2020} use suction cups to adhere to surfaces. However, underwater adhesion mediated by secreted liquids require the displacement of the water at the interface first and a spreading of the fluid on the substrate. One relatively simple approach is to use an air bubble around the adhesive organs similar to the air bubbles many secondary aquatic insects and spiders carry on their body for breathing underwater \cite{Seymour:2013}. This has been shown in a recent study by \citet{RN87} that female terrestrial green dock beetles \emph{Gastrophysa viridula} can attach quite well to surfaces underwater by using such an air bubble. Their naturally hydrophobic tarsal hairs trap the bubble around the pads when being submerged underwater, which de-wets the surface on contact. It has been hypothesised that a combination of capillary forces due the air bubble and hair secretions within the de-wetted area results in its adhesion underwater. However, it remained unclear if an air bubble is necessary for adhesion and what, if any, contribution it has to the adhesive force. The oily tarsal adhesive fluid found in insects alone might be sufficient in creating the necessary capillary adhesion even without a bubble, given that the fluid remains on the hair tips when submerged. In ladybug beetles, the tip of each seta secretes approximately one femtoliter of tarsal adhesive fluid by each step \cite{RN108}. The fluid's chemical composition in green dock beetles was identified to be an oil-containing mixture of mostly long chain hydrocarbons\cite{RN96} with traces
of triglycerides, fatty acids and cholesterol in ladybirds \emph{Hemisphaerota cyanea} \cite{RN221} and \emph{Epilachna vingtipunctuata} \cite{RN222}, rendering it immiscible with water.

The goal of this paper is to clarify the current understanding of underwater adhesion seen in terrestrial insects which use hairy pads and secrete an oily fluid for attachment. We used the ladybug beetle (\emph{Coccinella septempunctata}) as an animal model to first experimentally measure adhesion force of its individual pads in air and underwater conditions, both on smooth hydrophilic and hydrophobic glass surfaces. Male ladybug beetles were chosen since they possess adhesive pads having mostly flat discoidal tipped hairs, which allow them to show superior adhesion on hard surfaces compared to females \cite{RN145} and they can also walk underwater. Second, we developed a simple theoretical model considering capillary forces to predict the net adhesion force of a hairy pad under different conditions. The case of underwater adhesion was studied both in the presence and absence of a trapped bubble, to decouple the bubble's role in the insect's adhesion. Finally, we discuss key insights gained from our experiments and model with regards to understanding adhesion in other animals. We hope our study to provide new strategies to design bio-inspired materials that show good adhesive properties in both air and underwater conditions, similar to what has been previously reported for terrestrial beetles \cite{RN87}.

@@

 %The beetle's leg was constrained similar to the method described by Bullock et al \cite{RN19}.
An individual beetle was first carefully anaesthetised using small amounts of CO\textsubscript{2} sublimating
from a piece of dry ice and then glued with a small dollop of epoxy glue on its elytra to the underside of a heavy steel ball. The ball was held in a bracket which allowed free rotational movement of the ball in each direction, thus helping to align the suspended beetle over the substrate (see Fig.~\ref{fig:Setup}). The bracket with the ball and the beetle could be further positioned by manual micro-manipulators in all three axes before the experiments. One front left leg was carefully fixed at its tibia to a piece of soft solder wire coming off the steel ball using Blu Tack (Bostik Ltd., U.K.), allowing us to further align the leg to the substrate. Each leg of a male ladybug beetle has two hairy adhesive pads. For the test, we only allowed the distal pad to come into contact with the substrate thus minimising partial or bad contact of the other one. The distal pad was thus restrained by fixing its dorsal side to the wire using Blu Tack. The claws on the leg were also fixed to the wire using epoxy glue to prevent any further movement and to prevent the claws from touching the substrate (Fig.~\ref{fig:Setup} top-left inset). Care was taken to ensure the glue doesn't contaminate the rest of the tarsomeres. A small piece of non-sticky Teflon tape helped to keep the other legs tucked close to the body and avoided any interference during the adhesion test. After the measurements, the beetle was freed by carefully removing the epoxy glue and Blu Tack without harming it and set free.

@@

The vertical and lateral piezos were used simultaneously to perform approach-retract
adhesion tests with the substrate to get the pull-off force. However,
instead of a simple down-up motion, an additional 100 \textmu m lateral sliding motion in the proximal direction 
was introduced after the leg made contact, to ensure most of the hair tips align well with the substrate \cite{RN19}.
A further 10 \textmu m compression step (approach) set all hairs in slight compression which helped further contact
with the surface. Next, a short pause (1 s) removed any
viscoelastic effects before finally retracting the leg away from the
substrate. All approach, retract and lateral slide motion was done
at a speed of 62.5 \textmu m s\protect\textsuperscript{-1}. Ventral view video recordings
were used for contact area extraction while the side view imaging
was used to visually aid orienting the pad with the substrate before
a test.

@@

\begin{figure}[H]
\begin{centering}
\includegraphics[scale=0.5]{Figure1-Setup_schematic}
\par\end{centering}
\caption{\label{fig:Setup} Adhesion test setup (see text for details). Top-left inset shows a magnified cartoon of the beetle's leg constrained to a solder wire (grey) using Blu Tack (blue) and epoxy glue (orange). The recorded force data and
contact area of a distal pad are shown in the bottom-right plot, in which, the shaded
regions from left to right represent the distinct movement sequence: approach, lateral pull, approach, pause and retract, respectively. Negative force values
represent attraction and the minimum force peak during the final retraction
step is the adhesion force used for further analysis. An animated version of a typical force recording is available in the supplementary material (see Movie1).}
\end{figure}

@@

\begin{figure}[H]
\centering{}\includegraphics[scale=0.5]{Figure2-Expt_effect_of_contact}\caption{\label{fig:Effect-of-contact}Box-and-whisker plot showing
 adhesion force measurements of ladybug beetle's (\emph{Coccinella
septempuctata}) distal pad on untreated hydrophilic glass (blue) and hydrophobic PFOTS coated glass (red) substrates in air and underwater
conditions (n=5 per box). The two modes of contact during underwater experiments
are represented separately: \textquotedblleft\emph{bubble}\textquotedblright{}
and \textquotedblleft\emph{no bubble}\textquotedblright . The small diamonds represent outlier points. Crosses
represent theoretical predictions of adhesion force, while, circles
represent the contribution of the bubble itself, calculated from the
capillary bridge model (see text). In the model, hair diameter = 4 \textmu m,
pad diameter = 200 \textmu m, hair length = 40 \textmu m,
N\protect\textsubscript{hairs} = 500, V\protect\textsubscript{fluid}
= 4.2 fL and V\protect\textsubscript{bubble} = 1.2 nL. Interfacial
tension of the tarsal adhesive fluid in air and water were assumed to be
24 mN m\protect\textsuperscript{-1} and 48 mN m\protect\textsuperscript{-1} respectively and water surface tension is 72 mN m\protect\textsuperscript{-1}.}
\end{figure}

@@

\begin{figure}[H]
\includegraphics[width=0.7\linewidth]{Figure3-Model_schematic}
\caption{\label{fig:Model}The capillary bridge model of a hairy adhesive pad. The hairs make contact
with the substrate (hydrophilic or hydrophobic) in three modes: a) \emph{In air}, where the tarsal adhesive
fluid bridges are surrounded by air; b) \emph{Underwater: no bubble},
where the fluid bridges are fully surrounded by water; c)\emph{
Underwater: bubble}, where part of the fluid bridges are
inside the bubble while others are outside in water (see text for details). The corresponding
ventral view contact images of the beetle's pad seen during adhesion experiments are shown on the right.}
\end{figure}

@@

@@

The capillary force, $f$, is the sum of two contributions: surface
tension and Laplace pressure. Force
versus distance for a single capillary bridge was calculated by Surface
Evolver simulations\cite{RN206}  (see supplementary section S1 for details),
and used to obtain $F_{net}$ as a function of $d$ for each mode
of contact. The adhesion force of the complete hairy pad system was
then obtained from the minima of $F_{net}$, where negative force
values represent attraction.

We considered $f_{air}$ and $f_{water}$ to be distinct terms
because the capillary force by the tarsal adhesive fluid would be different
in air and underwater due to its different contact angle and interfacial
tension in each case. Using the Young-Dupr\textcyr{\`\cyre} equations
for each case of fluid-air, fluid-water and water-air interface, one
can derive the following relation for the contact angle of the tarsal adhesive
fluid underwater:

@@

\begin{table}[H]
\centering{}%
\begin{tabular}{|l|c|}
\hline 
Property & Value\tabularnewline
\hline 
\hline 
Contact area fraction, $\alpha$ & 0.1\tabularnewline
\hline 
Hair aspect ratio, $L/D_{h}$ & 10\tabularnewline
\hline 
Water surface tension ratio, $\gamma_{wa}/\gamma_{fa}$ & 3\tabularnewline
\hline 
Tarsal fluid-water interfacial tension ratio, $\gamma_{fw}/\gamma_{fa}$ & 2\tabularnewline
\hline 
Tarsal fluid size parameter, $\phi_{f}$ & 2\tabularnewline
\hline 
Hydrophilic substrate & $\theta_{fa}=6\lyxmathsym{\textdegree}$, $\theta_{wa}=24\lyxmathsym{\textdegree}$\tabularnewline
\hline 
Hydrophobic substrate & $\theta_{fa}=50\lyxmathsym{\textdegree}$, $\theta_{wa}=120\lyxmathsym{\textdegree}$\tabularnewline
\hline 
\end{tabular}\caption{\label{tab:Model-parameters}Fixed parameter values corresponding to the pad's geometry, 
tarsal fluid and substrate wetting properties used in the capillary bridge model}
\end{table}

@@

\begin{figure}[H]
\begin{minipage}[t]{0.5\columnwidth}%
\includegraphics[scale=0.5]{Figure4a-Single_bridge_fd}

\subcaption{Force-distance curves}%
\end{minipage}\hfill{}%
\begin{minipage}[t]{0.5\columnwidth}%
\includegraphics[scale=0.5]{Figure4b-Single_bridge_force_contribution}

\subcaption{Force contributions}%
\end{minipage}\caption{\label{fig:Single-bridge}Simulation of normalised capillary force of a single liquid
bridge in contact with a substrate and pinned to a circular perimeter
on top. Fluid size parameter, $\phi_{f}=2$. Negative force values
represents attraction. a) Force-distance curves are shown for different
contact angles of the liquid with the substrate. b) Adhesion forces,
calculated from the minima of the corresponding force-distance curves,
are plotted as a function of contact angle with the substrate, together
with its Laplace and surface tension components (equation S1 in supplementary section).
Simulation snapshots of the liquid meniscus corresponding to angles
6\textdegree{} and 150\textdegree{} are depicted.}
\end{figure}

The force-distance curves show a general trend of repulsive forces
at small distances (Figure \ref{fig:Single-bridge}a). This is a result
of the pinned contact line on the top. A limited volume is available
for the liquid to occupy when the gap distance is small, causing the
meniscus shape to bulge outwards near the pinned contact line. This
creates a net positive curvature, resulting in a positive Laplace
pressure and thus repulsion. Without pinning, the capillary forces
would have shown high attractive forces on a hydrophilic substrate\cite{RN93}.

>>>>

%% Author_tex.tex
%% V1.0
%% developed by Nova Techset
%%
%% This file describes the coding for COB.cls

\documentclass[vruler,JEB]{COB}%%%%where COB is the template name

%The authors can define any packages after the \documentclass{COB} command.

%\usepackage{amsmath} for dealing with mathematics,
%\usepackage{amsthm} for dealing with theorem environments,
%\usepackage{cite} %for dealing with citations
%\usepackage{hyperref} for linking the cross references
%\usepackage{graphics} for dealing with figures.
%\usepackage{algorithmic} for describing algorithms
%\usepackage{subfig} for getting the subfigures e.g., "Figure 1a and 1b" etc.
%\usepackage{url} It provides better support for handling and breaking URLs.

\usepackage{widetext-TI}
%
%\usepackage{babel}
%\usepackage[authoryear]{natbib}
%\usepackage{array}
%\usepackage{textcomp}
%\usepackage{url}
\usepackage{multirow}
%\usepackage{amsmath}
%\usepackage{graphicx}
%\usepackage{subscript}
%\usepackage[unicode=true,pdfusetitle,
% bookmarks=true,bookmarksnumbered=false,bookmarksopen=false,
% breaklinks=false,backref=false,colorlinks=false]
% {hyperref}
%
%\newtheorem{theorem}{Theorem}
%\newtheorem{condition}{Condition}
\bibliographystyle{jeb}
\newcommand{\lyxmathsym}[1]{\ifmmode\begingroup\def\b@ld{bold}
  \text{\ifx\math@version\b@ld\bfseries\fi#1}\endgroup\else#1\fi}
%% Because html converters don't know tabularnewline
\providecommand{\tabularnewline}{\\}
\newcommand \newblock{\textbf}
%The author can find the documentation of the above style file and any additional
%supporting files if required from "http://www.ctan.org"

% *** Do not adjust lengths that control margins, column widths, etc. ***

\supertitle{Research Article}

@@

\author{Pranav Sudersan$^{1}$, Michael Kappl$^{1}$, Bat-El Pinchasik$^{2}$, Hans-J\"{u}rgen Butt$^{1}$ and Thomas Endlein$^{1}$}

\address{\add{1}{Max Planck Institute for Polymer Research, Ackermannweg 10, Mainz, Germany}
\add{2}{School of Mechanical Engineering, Tel Aviv University, Tel Aviv-Yafo, Israel}}

\corres{(\email{endlein01@mpip-mainz.mpg.de}; \email{xxxx@xxxx.xxx.xx})}

\date{Received 11 May 2021; revised 11 May 2021} %CHECK DATE

\maketitle

\begin{abstract}
Many insects can climb smooth surfaces using hairy adhesive pads on their legs mediated by tarsal fluid secretions. It was previously shown that a terrestrial beetle can even adhere and walk underwater. The naturally hydrophobic hairs trap an air bubble around the pads, allowing the hairs to make contact to the substrate like in air. However, it remained unclear to what extent such an air bubble is necessary for underwater adhesion. To investigate the role of the bubble, we measured the adhesive forces in individual legs of live but constrained ladybug beetles underwater in the presence and absence of a trapped bubble and compared it with its adhesion in air. Our experiments revealed that on a hydrophobic substrate, even without a bubble, the pads show adhesion comparable to that in air. On a hydrophilic substrate, underwater adhesion is significantly reduced, with or without a trapped bubble. We modelled the adhesion of a hairy pad using capillary forces. Coherent with our experiments, the model demonstrates that the wetting properties of the tarsal fluid alone can determine the ladybugs'  adhesion to smooth surfaces in both air and underwater conditions and that an air bubble is not a prerequisite for their underwater adhesion. The study highlights how such a mediating fluid can serve as a potential strategy to achieve underwater adhesion via capillary forces, which could inspire artificial adhesives for underwater applications.
\end{abstract}

@@

@@

The question on how insects and other small animals climb smooth and slippery
surfaces has fascinated scientists for the past three centuries \citep{RN198,RN59}. We know that such animals are able to adhere by using specialised organs on their feet called adhesive pads. These adhesive pads can generally be described as either ``smooth'' or ``hairy''. Several insect orders including earwigs, flies, and beetles \citep{Gorb:2001b} but also several spiders \citep{Coddington:1991} and arboreal lizards \citep{Williams:1982} bear hairy pads. Hairy pads show 1) compliance to rough surfaces due to their lower effective modulus, 2) angle dependent adhesion due to asymmetric hair geometry and 3) self-cleaning capability \citep{RN20}, which makes them suitable to adhere to most surfaces reversibly. The hairs themselves (setae) can branch into smaller fibrillar units (spatulae) as seen in spiders and lizards but are typically undivided in most insects. The hairs in many insects can however exhibit different tip geometries, including discoidal, spatula shaped or pointed tips, and distributed throughout the pad depending on sex or species\citep{RN19}. Single seta force measurements revealed that discoidal shaped seta show larger pull-off forces than spatula shaped or pointed setae\citep{RN79}, illustrating the role of hair geometry in adhesion. Insect tarsal hairs secrete an adhesion-mediating fluid (``wet adhesion'') while spiders and geckos rely on their dry hairy pads for attachment (``dry adhesion''). In the ``wet adhesion'' case, fluid secretion can enforce adhesion through surface tension and viscous forces \citep{RN201,RN155,RN71}, while, ``dry adhesion'' relies mostly on van der Waals forces \citep{RN202}.

While most of the studies on insect adhesion focused on terrestrial species, underwater insect attachment is much rarer and has been relatively unexplored. Some aquatic insects like diving beetles \citep{Chen:2014} or midge larva \citep{Kang:2020} use suction cups to adhere to surfaces. However, underwater adhesion mediated by secreted liquids require the displacement of the water at the interface first and a spreading of the fluid on the substrate. One relatively simple approach is to use an air bubble around the adhesive organs similar to the air bubbles many secondary aquatic insects and spiders carry on their body for breathing underwater \citep{Seymour:2013}. This has been shown in a recent study by \citep{RN87} that female terrestrial green dock beetles \emph{Gastrophysa viridula} can attach quite well to surfaces underwater by using such an air bubble. Their naturally hydrophobic tarsal hairs trap the bubble around the pads when being submerged underwater, which de-wets the surface on contact. It has been hypothesised that a combination of capillary forces due the air bubble and hair secretions within the de-wetted area results in its adhesion underwater. However, it remained unclear if an air bubble is necessary for adhesion and what, if any, contribution it has to the adhesive force. The oily tarsal adhesive fluid found in insects alone might be sufficient in creating the necessary capillary adhesion even without a bubble, given that the fluid remains on the hair tips when submerged. In ladybug beetles, the tip of each seta secretes approximately one femtoliter of tarsal adhesive fluid by each step \citep{RN108}. The fluid's chemical composition in green dock beetles was identified to be an oil-containing mixture of mostly long chain hydrocarbons\citep{RN96} with traces
of triglycerides, fatty acids and cholesterol in ladybirds \emph{Hemisphaerota cyanea} \citep{RN221} and \emph{Epilachna vingtipunctuata} \citep{RN222}, rendering it immiscible with water.

The goal of this paper is to clarify the current understanding of underwater adhesion seen in terrestrial insects which use hairy pads and secrete an oily fluid for attachment. We used the ladybug beetle (\emph{Coccinella septempunctata}) as an animal model to first experimentally measure adhesion force of its individual pads in air and underwater conditions, both on smooth hydrophilic and hydrophobic glass surfaces. Male ladybug beetles were chosen since they possess adhesive pads having mostly flat discoidal tipped hairs, which allow them to show superior adhesion on hard surfaces compared to females \citep{RN145} and they can also walk underwater. Second, we developed a simple theoretical model considering capillary forces to predict the net adhesion force of a hairy pad under different conditions. The case of underwater adhesion was studied both in the presence and absence of a trapped bubble, to decouple the bubble's role in the insect's adhesion. Finally, we discuss key insights gained from our experiments and model with regards to understanding adhesion in other animals. We hope our study to provide new strategies to design bio-inspired materials that show good adhesive properties in both air and underwater conditions, similar to what has been previously reported for terrestrial beetles \citep{RN87}.

@@

 %The beetle's leg was constrained similar to the method described by Bullock et al \citep{RN19}.
An individual beetle was first carefully anaesthetised using small amounts of CO\textsubscript{2} sublimating
from a piece of dry ice and then glued with a small dollop of epoxy glue on its elytra to the underside of a heavy steel ball. The ball was held in a bracket which allowed free rotational movement of the ball in each direction, thus helping to align the suspended beetle over the substrate (see Fig.~\ref{fig:Setup}). The bracket with the ball and the beetle could be further positioned by manual micro-manipulators in all three axes before the experiments. One front left leg was carefully fixed at its tibia to a piece of soft solder wire coming off the steel ball using Blu Tack (Bostik Ltd., U.K.), allowing us to further align the leg to the substrate. Each leg of a male ladybug beetle has two hairy adhesive pads. For the test, we only allowed the distal pad to come into contact with the substrate thus minimising partial or bad contact of the other one. The distal pad was thus restrained by fixing its dorsal side to the wire using Blu Tack. The claws on the leg were also fixed to the wire using epoxy glue to prevent any further movement and to prevent the claws from touching the substrate (Fig.~\ref{fig:Setup} top-left inset). Care was taken to ensure the glue doesn't contaminate the rest of the tarsomeres. A small piece of non-sticky Teflon tape helped to keep the other legs tucked close to the body and avoided any interference during the adhesion test. After the measurements, the beetle was freed by carefully removing the epoxy glue and Blu Tack without harming it and set free.

@@

The vertical and lateral piezos were used simultaneously to perform approach-retract
adhesion tests with the substrate to get the pull-off force. However,
instead of a simple down-up motion, an additional 100 \textmu m lateral sliding motion in the proximal direction 
was introduced after the leg made contact, to ensure most of the hair tips align well with the substrate \citep{RN19}.
A further 10 \textmu m compression step (approach) set all hairs in slight compression which helped further contact
with the surface. Next, a short pause (1 s) removed any
viscoelastic effects before finally retracting the leg away from the
substrate. All approach, retract and lateral slide motion was done
at a speed of 62.5 \textmu m s\protect\textsuperscript{-1}. Ventral view video recordings
were used for contact area extraction while the side view imaging
was used to visually aid orienting the pad with the substrate before
a test.

@@

\begin{figure*}[!t]
\centering
\includegraphics[width=6in]{Figure1-Setup_schematic}%
\caption[]{Adhesion test setup (see text for details). Top-left inset shows a magnified cartoon of the beetle's leg constrained to a solder wire (grey) using Blu Tack (blue) and epoxy glue (orange). The recorded force data and
contact area of a distal pad are shown in the bottom-right plot, in which, the shaded
regions from left to right represent the distinct movement sequence: approach, lateral pull, approach, pause and retract, respectively. Negative force values
represent attraction and the minimum force peak during the final retraction
step is the adhesion force used for further analysis. An animated version of a typical force recording is available in the supplementary material (see Movie1).}
\label{fig:Setup}
\end{figure*}

%\begin{figure}
%\begin{centering}
%\includegraphics[width=3in]{Figure1-Setup_schematic}
%\par\end{centering}
%\caption{\label{fig:Setup} Adhesion test setup (see text for details). Top-left inset shows a magnified cartoon of the beetle's leg constrained to a solder wire (grey) using Blu Tack (blue) and epoxy glue (orange). The recorded force data and
%contact area of a distal pad are shown in the bottom-right plot, in which, the shaded
%regions from left to right represent the distinct movement sequence: approach, lateral pull, approach, pause and retract, respectively. Negative force values
%represent attraction and the minimum force peak during the final retraction
%step is the adhesion force used for further analysis. An animated version of a typical force recording is available in the supplementary material (see Movie1).}
%\end{figure}

@@

\begin{figure}
\includegraphics[width=3.5in]{Figure2-Expt_effect_of_contact}\caption{\label{fig:Effect-of-contact}Box-and-whisker plot showing
 adhesion force measurements of ladybug beetle's (\emph{Coccinella
septempuctata}) distal pad on untreated hydrophilic glass (blue) and hydrophobic PFOTS coated glass (red) substrates in air and underwater
conditions (n=5 per box). The two modes of contact during underwater experiments
are represented separately: \textquotedblleft\emph{bubble}\textquotedblright{}
and \textquotedblleft\emph{no bubble}\textquotedblright . The small diamonds represent outlier points. Crosses
represent theoretical predictions of adhesion force, while, circles
represent the contribution of the bubble itself, calculated from the
capillary bridge model (see text). In the model, hair diameter = 4 \textmu m,
pad diameter = 200 \textmu m, hair length = 40 \textmu m,
N\protect\textsubscript{hairs} = 500, V\protect\textsubscript{fluid}
= 4.2 fL and V\protect\textsubscript{bubble} = 1.2 nL. Interfacial
tension of the tarsal adhesive fluid in air and water were assumed to be
24 mN m\protect\textsuperscript{-1} and 48 mN m\protect\textsuperscript{-1} respectively and water surface tension is 72 mN m\protect\textsuperscript{-1}.}
\end{figure}

@@

@@

\begin{figure}
\includegraphics[width=3.5in]{Figure3-Model_schematic}
\caption{\label{fig:Model}The capillary bridge model of a hairy adhesive pad. The hairs make contact
with the substrate (hydrophilic or hydrophobic) in three modes: a) \emph{In air}, where the tarsal adhesive
fluid bridges are surrounded by air; b) \emph{Underwater: no bubble},
where the fluid bridges are fully surrounded by water; c)\emph{
Underwater: bubble}, where part of the fluid bridges are
inside the bubble while others are outside in water (see text for details). The corresponding
ventral view contact images of the beetle's pad seen during adhesion experiments are shown on the right.}
\end{figure}

@@

The capillary force, $f$, is the sum of two contributions: surface
tension and Laplace pressure. Force
versus distance for a single capillary bridge was calculated by Surface
Evolver simulations\citep{RN206}  (see supplementary section S1 for details),
and used to obtain $F_{net}$ as a function of $d$ for each mode
of contact. The adhesion force of the complete hairy pad system was
then obtained from the minima of $F_{net}$, where negative force
values represent attraction.

We considered $f_{air}$ and $f_{water}$ to be distinct terms
because the capillary force by the tarsal adhesive fluid would be different
in air and underwater due to its different contact angle and interfacial
tension in each case. Using the Young-Dupr\'{e} equations
for each case of fluid-air, fluid-water and water-air interface, one
can derive the following relation for the contact angle of the tarsal adhesive
fluid underwater:

@@

%\begin{table}
%\centering{}%
%\begin{tabular}{|l|c|}
%\hline 
%Property & Value\tabularnewline
%\hline 
%\hline 
%Contact area fraction, $\alpha$ & 0.1\tabularnewline
%\hline 
%Hair aspect ratio, $L/D_{h}$ & 10\tabularnewline
%\hline 
%Water surface tension ratio, $\gamma_{wa}/\gamma_{fa}$ & 3\tabularnewline
%\hline 
%Tarsal fluid-water interfacial tension ratio, $\gamma_{fw}/\gamma_{fa}$ & 2\tabularnewline
%\hline 
%Tarsal fluid size parameter, $\phi_{f}$ & 2\tabularnewline
%\hline 
%Hydrophilic substrate & $\theta_{fa}=6\lyxmathsym{\textdegree}$, $\theta_{wa}=24\lyxmathsym{\textdegree}$\tabularnewline
%\hline 
%Hydrophobic substrate & $\theta_{fa}=50\lyxmathsym{\textdegree}$, $\theta_{wa}=120\lyxmathsym{\textdegree}$\tabularnewline
%\hline 
%\end{tabular}\caption{\label{tab:Model-parameters}Fixed parameter values corresponding to the pad's geometry, 
%tarsal fluid and substrate wetting properties used in the capillary bridge model}
%\end{table}

\begin{table}[!t]
\processtable{Fixed parameters corresponding to the pad's geometry, 
tarsal fluid and substrate wetting properties used in the capillary bridge model \label{tab:Model-parameters}}
{\begin{tabular*}{3.5in}{@{\extracolsep{\fill}}lllll@{}}
\hline
\TCH{Property} & \TCH{Value} \\
\hline
Contact area fraction, $\alpha$ & 0.1\\
Hair aspect ratio, $L/D_{h}$ & 10\\
Water surface tension ratio, $\gamma_{wa}/\gamma_{fa}$ & 3\\
Tarsal fluid-water interfacial tension ratio, $\gamma_{fw}/\gamma_{fa}$ & 2\\
Tarsal fluid size parameter, $\phi_{f}$ & 2\\
\multirow{2}{*}{Hydrophilic substrate wetting} &  $\theta_{fa}=6\lyxmathsym{\textdegree}$\\
    & $\theta_{wa}=24\lyxmathsym{\textdegree}$\\
\multirow{2}{*}{Hydrophobic substrate wetting} &  $\theta_{fa}=50\lyxmathsym{\textdegree}$\\
    & $\theta_{wa}=120\lyxmathsym{\textdegree}$
\end{tabular*}}{}
\end{table}

@@

\begin{figure*}[!t]
\centering
\subfloat[Force-distance curves]{\includegraphics[width=3in]{Figure4a-Single_bridge_fd}\label{fig_first_case}}%
\hskip3pc
\subfloat[Force contributions]{\includegraphics[width=3in]{Figure4b-Single_bridge_force_contribution}\label{fig_second_case}}%
\caption[]{Simulation of normalised capillary force of a single liquid
bridge in contact with a substrate and pinned to a circular perimeter
on top. Fluid size parameter, $\phi_{f}=2$. Negative force values
represents attraction. a) Force-distance curves are shown for different
contact angles of the liquid with the substrate. b) Adhesion forces,
calculated from the minima of the corresponding force-distance curves,
are plotted as a function of contact angle with the substrate, together
with its Laplace and surface tension components (equation S1 in supplementary section).
Simulation snapshots of the liquid meniscus corresponding to angles
6\textdegree{} and 150\textdegree{} are depicted.}
\label{fig:Single-bridge}
\end{figure*}

%\begin{figure}
%%\begin{minipage}[t]{0.5\columnwidth}%
%\includegraphics[scale=0.5]{Figure4a-Single_bridge_fd}
%
%\subcaption{Force-distance curves}%
%\end{minipage}\hfill{}%
%\begin{minipage}[t]{0.5\columnwidth}%
%\includegraphics[scale=0.5]{Figure4b-Single_bridge_force_contribution}
%
%\subcaption{Force contributions}%
%\end{minipage}
%\caption{\label{fig:Single-bridge}Simulation of normalised capillary force of a single liquid
%bridge in contact with a substrate and pinned to a circular perimeter
%on top. Fluid size parameter, $\phi_{f}=2$. Negative force values
%represents attraction. a) Force-distance curves are shown for different
%contact angles of the liquid with the substrate. b) Adhesion forces,
%calculated from the minima of the corresponding force-distance curves,
%are plotted as a function of contact angle with the substrate, together
%with its Laplace and surface tension components (equation S1 in supplementary section).
%Simulation snapshots of the liquid meniscus corresponding to angles
%6\textdegree{} and 150\textdegree{} are depicted.}
%\end{figure}
